Designing Turk Experiments for Visual Statistical Inference

### 2013-06-12 paper_turk.tex
conclusion started

\begin{figure}[hbtp]
   \centering
       \scalebox{.4}{\includegraphics{turk_web.png}}
       \caption{A sample data collection form. Lineups are presented at random for evaluations by the turk workers.}
       \label{fig:turk_web}
\end{figure}

@@

\section{Conclusion}

>>>>

\begin{figure}[hbtp]
   \centering
       \scalebox{.4}{\includegraphics{turk_web.pdf}}
       \caption{A sample data collection form. Lineups are presented at random for evaluations by the turk workers. Scalable Vector Graphics (SVG) is used so that observer can click on the lineup to pick certain plot.}
       \label{fig:turk_web}
\end{figure}

@@

\section{Conclusion} This paper presents a complete solution to the problem of designing a simulation experiment for lineup and recruiting people to get the lineups evaluated. The proposed online application design provides flexibility to control how the multiple lineups would be presented to a observer. It also gives added benefit to record timing of the evaluations. Scalable Vector Graphics (SVG) is used so that observer can click on the lineup to pick certain plot. This also made the multiple plot selection from a lineup easier and convenient. Multiple online experiments are done using this web application and result suggests that the application worked as planned.

The web application is designed such a way that it still produces simple task for the worker who are used to doing so from MTurk. But it gives many flexibilities to the researcher who need lineups to be evaluated as per complex experimental requirement.
